Extreme Value Chapter

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
argh

```{r fig.height=3, fig.width=7}
nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  group_by(thresh_tests, samp_n_tests) %>% 
  summarize(Eval_theta_hat = mean(log_St_hat2),
            theta = mean(theta),
            bias = Eval_theta_hat - theta) %>% 
  ggplot(., aes(y = bias, x = thresh_tests)) +
  geom_jitter(aes(color = samp_n_tests), size = 3, alpha = 0.9, width = 0.1) +
  geom_hline(yintercept = 0, color = "grey") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = "Bias", title = "GLM Lomax") +
  theme_bw()

@@

```{r fig.height=10, fig.width=10}

corr_a %>% 
  right_join(., thetas) %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
  facet_wrap(~labelsamp) +
  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
  geom_point(aes(y = log(theta)), size = 3, shape = 18, color = theta_color, show_guide = FALSE) +
  scale_fill_manual(values = c("grey47", "white"), name = "") +
  labs(x = "Long-distance level", y = "Estimated theta", title = corr_a$correctiontype[1]) +
  theme_bw() +
  scale_y_continuous(limits = quantile(corr_a$value, c(0.1, 0.9))) +
  theme(legend.position = "right") -> a

corr_b %>% 
  right_join(., thetas) %>%
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
  facet_wrap(~labelsamp) +
  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
  geom_point(aes(y = log(theta)), size = 3, shape = 18, color = theta_color, show_guide = FALSE) +
  scale_fill_manual(values = c("grey47", "white"), name = "") +
  labs(x = "Long-distance level", y = "Estimated theta", title = corr_b$correctiontype[1]) +
  theme_bw() +
  scale_y_continuous(limits = quantile(corr_b$value, c(0.1, 0.9))) +
  theme(legend.position = "right") -> b

>>>>

```{r fig.height=2.5, fig.width=5}
nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  group_by(thresh_tests, samp_n_tests) %>% 
  summarize(Eval_theta_hat = mean(log_St_hat2),
            theta = mean(theta),
            bias = Eval_theta_hat - theta) %>% 
  ggplot(., aes(y = bias, x = thresh_tests)) +
  geom_jitter(aes(color = samp_n_tests), size = 3, alpha = 0.9, width = 0.1) +
  geom_hline(yintercept = 0, color = "grey") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = "Bias", subtitle = "GLM Lomax") +
  theme_bw()

@@

```{r fig.width=12, fig.height=6}
nonpar_glm %>% 
  mutate(Original = theta_hat - theta,
         # Corrected = log_theta_stars - theta,
         Corrected = theta_bar - theta,) %>% 
  dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
  pivot_longer(cols = c(Original, Corrected), names_to = "type") %>% 
  filter(., !is.infinite(value)) %>% 
  # filter(., thresh_tests < 500) %>% 
  mutate(thresholdsep = factor(ifelse(thresh_tests<500, "lower dist", "extremes"), levels = c("lower dist", "extremes"))) %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  mutate(onelinelabel = paste0(labelsamp,"-",thresholdsep)) %>% 
  ggplot(., aes(x = thresh_tests, y = value, fill = samp_n_tests, color = type)) +
  facet_wrap(~onelinelabel, nrow = 2, scales = "free") +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_color_manual(values = c("black", "grey"), name = " ") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Distance level", y = "Estimates of theta", subtitle = " ") +
  theme_bw()

```{r fig.height=6, fig.width=12}

corr_a %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
  facet_wrap(~labelsamp, nrow=1) +
  geom_hline(yintercept = 0, color = "red") +
  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
  scale_fill_manual(values = c("grey47", "white"), name = "") +
  labs(x = "Distance level", y = "Estimated theta", title = corr_a$correctiontype[1]) +
  theme_bw() +
  scale_y_continuous(limits = quantile(corr_a$value, c(0.1, 0.9))) +
  theme(legend.position = "right") -> a

corr_b %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
  facet_wrap(~labelsamp, nrow=1) +
  geom_hline(yintercept = 0, color = "red") +
  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
  scale_fill_manual(values = c("grey47", "white"), name = "") +
  labs(x = "Distance level", y = "Estimated theta", title = corr_b$correctiontype[1]) +
  theme_bw() +
  scale_y_continuous(limits = quantile(corr_b$value, c(0.1, 0.9))) +
  theme(legend.position = "right") -> b
